The shape of dark matter halos in the AURIGA simulations

### 2019-02-14 Paper/paper.tex
edit

\title[MW DM halo shape in AURIGA]{The expected shape of the Milky Way's Dark Matter halo}

\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\', Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
Germany.\\
}

@@

\subsection{The radial tendency of axial ratios}

We found that most halos exhibit a monotonically-increasing somewhat
steady tendency of its axial ratios $b/a,c/a$  with radius, which is
well exemplified on figure \ref{fig:DM_MHD}. There are some special
cases in which fluctuations of the local DM density field affects this
relation, but in average, this monotonic and steady tendency is clear
and can be consulted on table \ref{table:DM table}. To ilustrate the
average behavior, as well as some peculiarities, we resume the results
of the 30 auriga simulations on the figure \ref{fig:Triax_DM} where
each shape represents a point in the triaxiality plane $c/a$ Vs
$b/a$. Check Vera-ciro onthis.

\begin{figure}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (DM only)
   Each dot represents the shape characterization of each halo at the 2 times the virial radius and a  1/16 fraction of the virial radius differentiated by color.
  Errorbar shows median and errors for each sampled radii.
  Conclusion: DM halos are rounder on the outskirts}
  \label{fig:Triax_DM}
\end{figure}

@@

\begin{figure}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
  \caption{Shape of each halo on the plane $c/a$ Vs $b/a$. (MHD only)
   Each dot represents the shape characterization of each halo at the
   2 times the virial radius and a  1/16 fraction of the virial radius
   differentiated by color. 
  Errorbar shows median and errors for each sampled radii.
  Conclusion: MHD halos are more oblate on the outer skirts: b/a
  changes while c/a remains practically constant (on average)}
  \label{fig:Triax_MHD}
\end{figure}

>>>>

\title[Dark Matter halo shape in the AURIGA simulations]{The shape of dark matter
  halos in the AURIGA simulations}  
\author[Jesus Prada,  Jaime E. Forero-Romero, Volker Springel ]{
Jesus Prada,$^{1}$\thanks{E-mail: jd.prada1760@uniandes.edu.co}
Jaime E. Forero-Romero,$^{1}$
Volker Springel$^{2}$
\\
% List of institutions
$^{1}$Departamento de F\'sica, Universidad de los Andes, Cra. 1 No.
18A-10, Edificio Ip, Bogot\', Colombia.\\
$^{2}$Heidelberg Institute for Theoretical Studies, Schloss-Wolfsbrunnenweg 35, D-69118 Heidelberg
Germany.\\
}

@@

Figure \ref{fig:triax_DM} summarizes this comparizon for all 30 halos
in the Level 3 simulations. 
Measurements at $R_{\rm vir}/16$ are represented by circlse while squares 
are measurements at $R_{\rm vir}$. 
All halos, except two, show that outer regions rounder than inner
regions.
The exceptions are cases where a merging substructures near  the
halo's center give rise to perturbed axial ratios measurments. 
Figure \ref{fig:triax_HDM} shows the same information, this time for
the MHD simulations. 
The main radial trend continues to hold, albet less pronounced; halos
in MHD simulations are in general rounder than their DM counterparts
and the increased roundness in outer regions is less pronounced on
average.

This situation is summarized Table \ref{table:shape}
We summarize these resulta in Table \ref{table:shape}

\begin{figure}
\includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_DM.png}
\caption{Axial ratios for the 30 halos in the Level 3 DM simulations.
   Each dot represents the shape characterization of each halo at the 2 times the virial radius and a  1/16 fraction of the virial radius differentiated by color.
  Errorbar shows median and errors for each sampled radii.
  Conclusion: DM halos are rounder on the outskirts {\bf Esto necesita
  correccion. Debe ser a R1/16 y R (no 2R!)}}
  \label{fig:triax_DM}
\end{figure}

\begin{figure}
 \includegraphics[width=0.9\columnwidth]{./pics/Triaxial_Plane/Triax_MHD.png}
  \caption{Axial ratios for the 30 halos in the Level 3 MHD
    simulations. DM halos are rounder at larger radii than small radii. {\bf Esto
      necesita correccion para que tambien sea a 
      R1/16 y R.}}
  \label{fig:triax_MHD}
\end{figure}

@@
